---
title: "Alcohol vs Seat choice"
author: "Jennifer Nava"
date: "June 7,2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
```{r}

## Now add in boxplot
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```

It appears that the people in the back consume more alcohol than the people who sit in the middle and front. 75% of people who sit in the back drink more than people sitting in the middle and front. 

  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
It seems, that the people in the back seats drink an average of 8.5 drinks and the people that sit in the front drink an average of 1.8 drinks. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We will reject this hypothesis, but we will seek clarification on which rows were different from other rows. 


```{r}
plot(TukeyHSD(model1))
```

Using the Turkey plot box we can tell that that the front is different from the back, and the middle is different from the back. However there is no difference between the middle and the front. 


##Conclusion


Because the categorical variable has; more than 2 leves, we have to use anova, not a t-test. the anova showed there is a difference in alcohol consumption among the seat locations; Tukey HSD show that the differences were in the back row, and not much different comprared to the middle and front. 
